An Efficient Minibatch Acceptance Test for Metropolis-Hastings

### 2016-07-18 nips_2016.tex
mnist sim

We would like to sample from the posterior distribution of $\theta$
which is a normal distribution centered on the sample mean, and with
variance $1/N$.  The target distribution is therefore
$\mathcal{N}(\mu,1/N)$ where $\mu$ is the sample mean, and $\mathcal{N}(\mu,\sigma^2)$ is a
normal distribution with mean $\mu$ and variance $\sigma^2$.  An efficient
proposal distribution has the same variance as the target distribution
$\mathcal{N}(\theta'-\theta,1/N)$, so we take $q(\theta'\mid\theta) =
\phi((\theta'-\theta)N)$, where $\phi(x)$ is the Normal density
function with zero mean and unit variance. This proposal is symmetric
$q(\theta'\mid\theta)=q(\theta\mid\theta')$, and we assumed uniform
prior for $\theta$, so $\psi(u,\theta',\theta)$ reduces to $\log
u$.

>>>>

We would like to sample from the posterior distribution of $\theta$
which is a normal distribution centered on the sample mean, and with
variance $1/N$.  The target distribution is therefore
$\mathcal{N}(\mu,1/N)$ where $\mu$ is the sample mean, and $\mathcal{N}(\mu,\sigma^2)$ is a
normal distribution with mean $\mu$ and variance $\sigma^2$.  An efficient
proposal distribution has the same variance as the target distribution in one dimension
\cite{OptimalScaling01}, so take the proposal
$\mathcal{N}(\theta'-\theta,1/N)$, which is implemented as $q(\theta'\mid\theta) =
\phi((\theta'-\theta)N)$, where $\phi(x)$ is the Normal density
function with zero mean and unit variance. This proposal is symmetric
$q(\theta'\mid\theta)=q(\theta\mid\theta')$, and we assumed uniform
prior for $\theta$, so $\psi(u,\theta',\theta)$ reduces to $\log
u$.
